{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-27 paper/paper.tex
added note about reflexsive, transitive closure of \leadsto_{conc}
be more explicit

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$.

@@

So the state $s$ evaluates according to a history $h$ to a final global memory $\mu$ iff there is a
sequence of concurrent executions that terminates (i.e. there are no active threads) and has the
global memory $\mu$.

>>>>

The next thing introduced are the security levels. We assume the attacker
'is' a level $k$. From this assumption we can reduce every set of security levels
w.l.o.g into $\{low, high\}$, where $low < high$, by mapping elements
that are no more sensitive than $k$ to $low$ and all other elements
-- including incomparable ones -- to $high$.

@@

So the state $s$ evaluates according to a history $h$ to a final global memory $\mu$ iff there is a
sequence of concurrent executions that terminates (i.e. there are no active threads) and has the
global memory $\mu$. $\leadsto_{conc}^*$ is the reflexive and transitive closure of of $\leadsto_{conc}$.
